The Dynamics of Anthropomorphism in Human-Robot Interaction

### 2014-04-03 paper.tex
Rewritten section 2.3

\subsection{Terminology and understandings used in this article}

We propose to use the term \textbf{anthropomorphism} to describe a social phenomenon, which arises in an interaction between a human agent and a non-human agent, \eg a robot (see Figure \ref{fig:anthropofig}). The term anthropomorphism can be used to refer to people's tendency to \textit{perceive} human-like characteristics in non-human agents (or artifacts), but also to refer to the observable effect of a person \textit{ascribing} or \textit{attributing} such human-like characteristics to the agent or artifact. Further, anthropomorphism might also be observable in a human's behavior / actions toward a non-human agent. The common point here is that anthropomorphism is always performed by the human (either in real or imagined).

However, the term anthropomorphism should \textit{not} be used to refer to the design of a non-human agent or artifact. This would violate the understanding of anthropomorphism arising in an interaction. To refer to an imitation of human-like form in the \textit{form} of artificial agents, we propose to use the term  \textbf{anthropomorphic design}. We found that in literature, this distinction is not always done, which is a major source of confusion.

In the following, we might use the terms \textit{form} and \textit{design} interchangeably. Using the term \textit{form} to describe the design of an artifact, we refer 
not only to the shape (how it looks like) but to the total 
expression of the artifact \citep{bartneck_shaping_2004}. \cite{disalvo_hug:_2003} 
argues that \textit{form} includes a product's physical shape, materials, and 
behavioral qualities. The behavioral aspect is of special importance for interactive 
systems that show some degree of autonomy (independence).
Several categories of anthropomorphic form can be classified, but there is no 
common agreement on the borders and transitions between these categories: 
anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}.

\begin{figure}
    \centering
    \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
    \caption{Anthropomorphism is a social phenomenon which arises in an interaction between a human agent and a non-human agent. The two agents are the main \textit{players} \hl{(or elements?)} of the interaction, and consequently one can apply two main perspectives when trying to explain anthropomorphism: a human-centered and an artifact-centered perspective (grey triangles). There are several person- and artifact-related factors that determine \hl{(or influence / impact on?)} anthropomorphism. Further, the context / situation in which the interaction occurs plays a role.}

>>>>

\subsection{Our acception of anthropomorphism and related terminology}

We use the term \textbf{anthropomorphism} to describe the \emph{psychological}
phenomenon, which arises in the \emph{social context} of an interaction between
a human agent and a non-human agent, in our case, a robot (see Figure
\ref{fig:anthropofig}). We use this term to refer to both people's tendency to
\textit{perceive} human-like characteristics, and to the tendency to
\textit{ascribe} or \textit{attribute} such human-like characteristics to the
agent or artifact. Besides, we call {\bf anthropomorphic effects} the
\emph{observable manifestations} of anthropomorphism, \ie the human's behaviors
and actions toward a non-human agent that reflect the underlying cognitive
process of anthropomorphizing.

However, we should \textit{not} use the term \emph{anthropomorphism} to refer to
the design of a non-human agent or artifact. To refer to an imitation of
human-like form in the \textit{design} of artificial agents, we use the term
\textbf{anthropomorphic design}. This explicit terminology prevents the commonly
encountered confusion between anthropomorphism as a psychological, subjective
phenomenon, and the external, objective factors that \emph{influence} the
phenomenon itself.

In the following, we might use the terms \emph{form} and \emph{design}
interchangeably. Note that the terms \textit{form} or {\it design} do not only
refer to the shape (how it looks like) but to the total expression of the
artifact~\citep{bartneck_shaping_2004}. \citet{disalvo_hug:_2003} argues that
\textit{form} includes the physical shape, materials, and behavioral qualities
of the product. The behavioral aspect is of special importance for interactive
systems that show some degree of autonomy (independence).  Several categories of
anthropomorphic form exist, with no common agreement on the borders and
transitions between those: anthropomorphic, zoomorphic, caricatured, functional
\citep{fong_survey_2003}.

\begin{figure}
    \centering
    \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
    \caption{Anthropomorphism is a psychological phenomenon which arises in a
        social context, during an
    interaction between a human agent and a non-human agent. One can take two main perspectives when trying to explain
    anthropomorphism: a human-centered and an artifact-centered perspective (grey
    triangles). Several external factors influence the anthropomorphism
    phenomenon. Person- and artifact-related ones, but also related to the
context of use as well as the actual time spend interacting with the robot.}
